---
title: "REC Center Report"
author: "Office of Research, Analysis, and Reporting"
date: r Sys.Date()
output: word_document
---

```{r setup, include = F}
# This "chunk" of code sets up the rest of the script and loads required packages
options(java.parameters = "-Xmx16G")
library(tidyverse)
library(lubridate)
library(haven)
library(knitr)
library(rmarkdown)

# install.packages("RStata")
# stata(<name of dofile>, path, Stata version)

# The snippet below is a yaml header that captures metadata that affect the document output

```

`r lubridate::month(now(), label = T, abbr = F)` `r year(now())`: Monthly Internal Report

### Summary of Performance
```{r, warning = F, echo = F, message = F}
# Set the directory and read in the file
setwd("X:/disengaged_youth/Automate REC reports/Analysis/4_Version04/Monthly Report/Output/0919 September 2019/")
summary = readxl::read_excel("16 - 24, No Credential, Not Enrolled_Monthly_REC_Report_Aug2019.xlsx",
      sheet = "Summary_of_Performance") %>% 
  mutate(
    performance_metric = case_when(
      performance_metric == "initial_intake" ~ "Short Intakes",
      performance_metric == "full_intake" ~ "Full Intakes",
      performance_metric == "first_placement" ~ "School Enrollments",
      performance_metric == "first_completion" ~ "Completions (Total)",
      T ~ str_to_title(str_replace_all(str_c("-    ", performance_metric), "_", " "))
    )
  )

# Reformat the variable names to make them more reader-friendly
names(summary) = str_to_title(str_replace_all(names(summary), "_", " "))

# Display the table
kable(summary)

# How would we change the values of the `Performance Metric` variable? 
# What observations should we drop? 
# What if we want to rename the `Last Month` variable as the actual month name (rather than just "Last Month")

```

### FY`r str_sub(year(now()) - 1, -2, -1)`: Weighted "Stick Rates" (averaged over FY18Q1 - FY19Q1)

```{r stick_rates, warning = F, echo = F, message = F}
# Set directory and load data
setwd("X:/disengaged_youth/Automate REC reports/Analysis/4_Version04/Monthly Report/Output/0919 September 2019/")
stick_rate = readxl::read_excel("16 - 24, No Credential, Not Enrolled_Monthly_REC_Report_Aug2019.xlsx", 
      sheet = "Stick_Rates") %>% 
  # Drop variables not in the table
  select(client_status, perc_stuck_180, perc_stuck_360) %>%
  # Keep only the observations we want
  filter(str_detect(client_status, "Active")) %>% 
  # Tidy up output
  mutate_at(
    vars(starts_with("perc")),
    funs(str_c(round(100 * ., 2), "%"))
  )
  
# Tidy up names
names(stick_rate) = str_to_title(str_replace_all(names(stick_rate), "_", " "))

# Display table
kable(stick_rate)

# How can we make the quarters dynamic (above)?
# How can we make the date dynamic (below)?
# Adding footnotes? 

```

### Demographics and Barriers since Opening (Oct. 20, 2014)

```{r demos, echo = F, message = F, warning = F}
setwd("X:/disengaged_youth/Automate REC reports/Analysis/4_Version04/Monthly Report/Output/0919 September 2019/")
summary = readxl::read_excel("16 - 24, No Credential, Not Enrolled_Monthly_REC_Report_Aug2019.xlsx",
      sheet = "Summary_of_Performance") %>% 
  mutate(
    performance_metric = case_when(
      performance_metric == "initial_intake" ~ "Short Intakes",
      performance_metric == "full_intake" ~ "Full Intakes",
      performance_metric == "first_placement" ~ "School Enrollments",
      performance_metric == "first_completion" ~ "Completions (Total)",
      T ~ str_to_title(str_replace_all(str_c("-    ", performance_metric), "_", " "))
    )
  )
```

Metric           | Last Month
---------------- | -------------
`r summary[1,1]` | `r summary[1, 2]`[^1]
[^1]: Insert footnote 

### Educational Outcomes in FY19 (Since Oct. 1, 2018)

The following table represents the median length of time () (number of days) between full intake and enrollment:

```{r }
# Table
```

### Referrals in FY19 (Since Oct. 1, 2018)
Overall, the ReEngagement Center has received `r ` referrals since Oct. 1, 2018.